\documentclass{report} % can be changed to article 

% imports

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[normalem]{ulem}
\usepackage[margin=1.5in]{geometry} % margin can be changed
\usepackage{changepage}
\usepackage{mdframed}
\usepackage{xcolor}
\usepackage{hyperref}

% environments

\newmdenv[
  topline=false,
  bottomline=false,
  rightline=false,
  skipabove=\topsep,
  skipbelow=\topsep
]{siderules}

\newcommand{\aparte}[2]{
  \vspace{0.5em}\noindent
  \begin{adjustwidth}{24pt}{0pt}
    \begin{siderules}
      \leavevmode\reversemarginpar{\raggedleft \textit{#1}} #2
    \end{siderules}
  \end{adjustwidth}
  \vspace{0.75em}
}

\newcommand{\sep}{
  \begin{center}
    \noindent\rule{0.35\textwidth}{0.5pt}
  \end{center}
}

% configs

\def\labelitemi{\ensuremath{\triangleright}}
\renewcommand{\theenumi}{\small {(\roman{enumi})}}
\definecolor{blueish}{RGB}{80, 150, 150}
\definecolor{redish}{RGB}{160, 70, 60}
\renewcommand{\emph}[1]{{\color{blueish} #1}}

% specific algebra stuff

\AtBeginEnvironment{pmatrix}{\setlength{\arraycolsep}{3pt}}

\newcommand{\tot}{\ensuremath\varphi}
\newcommand{\gen}[1]{\ensuremath\langle #1 \rangle}
\newcommand{\Orb}{\ensuremath\operatorname{Orb}}
\newcommand{\Stab}{\ensuremath\operatorname{Stab}}
\newcommand{\sgn}{\ensuremath\operatorname{sgn}}
\newcommand{\ord}{\ensuremath\operatorname{ord}}
\newcommand{\lcm}{\ensuremath\operatorname{lcm}}
\renewcommand{\mod}{\ensuremath\operatorname{mod}}
\renewcommand{\emptyset}{\varnothing}
\renewcommand{\bar}{\overline}

% specific maths stuff
\newtheorem*{theorem*}{Proposition}
\newtheorem*{unnumthm}{Theorem}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{plain}
\newtheorem{example}{Example}
\newtheorem{definition}[theorem]{Definition}

\title{Algebra - MATH310}
\author{Jacopo ``quartztz'' Moretti}
\date{January 2024}

\begin{document}
  \maketitle

  \chapter*{Preface}
  Helo! I'm Jack :3.

  I'm a student that needs to type out courses in order to make sure they properly understand them. So I put them out into the world! They might help you more than they help me :D. They are given as they are, with no guarantee of quality but guarantee of goodwill, bla bla bla. You know the gist of it. 

  \section*{Elements of notation}

  The group operation for a group $G$ will usually be denoted $\cdot_G$, and its neutral element will be $e_G$. The index will be removed when it can be inferred from context. 

  For now, I'll denote $\mathbf{n} = \{1, ..., n\}$, because it's clunky to type and it's my notes, goddamnit. I might change it back at the end.

  Also sometimes I get caught up and I use the weird (though admittedly concise) notation:
  \begin{center}
    ``... consider an $0 \neq a \in A$''
  \end{center}
  which is to be read as ``consider an $a$ in $A$ such that it is non zero''. Sorry for the confusion.

  \tableofcontents

  \pagebreak

  \input{chapters/chapter1.tex}
  \input{chapters/chapter2.tex}
  \input{chapters/chapter3.tex}
  \input{chapters/chapter4.tex}

  \appendix
  
  \input{chapters/appendixA.tex}
  \input{chapters/appendixB.tex}
  \input{chapters/appendixC.tex}
\end{document}